---
title: "Day 3 Homework"
output: html_document
---

1. Identify a column in your data that *should* be a factor (whether it is or not). Check to see whether R is already treating it as a factor, and if not, convert it into a factor.

```{r}
rm(list = objects())
data <- read.csv("Brockett_HW_Dataset.csv", header = TRUE)
summary(data)

# Trial type (Go vs. Stop) should be a factor and using summary() it appears that R is treating it as such

```

2. What are the levels of the factor? How many occurrences of each level are there in the data?
   
```{r}

levels(data$trial_type)
summary(data)
xtabs(~ trial_type, data)

# The levels of the factor are 'go' and 'stop' and there are 536 occurrences of each level

```

3. Create a new column that is a numeric "version" of the factor column, using `as.numeric()`. Use `xtabs()` to see how the values of these columns line up.

```{r}

data$trial_type_num <- as.numeric(data$trial_type)
xtabs(~ trial_type + trial_type_num, data)

# With trial_type as a number, GO is 1 and STOP is 2

```

4. Create another column that is a copy of the factor column. Now, recode this new column so that the factor levels have new names. 
  (e.g., if you have a factor with levels "A" and "B", you could make a new column that had "condition A" and "condition B" as the level names instead)

```{r}

data$trial_type_new <- data$trial_type # create new column

levels(data$trial_type_new) <- c("A", "B") # rename levels in the new column A and B (previously GO and STOP)
# - the reason this function works is because there is actually a function called "levels() <- " which allows you to
#   reasign names/ values. Similar to colnames() which has colnames() and "colmanes() <- "

head(data) # check that factors are renamed

xtabs(~ trial_type + trial_type_new, data) # check that factors are renamed relative original column

```

5. Change the order of the levels in your new factor, using three different methods:
  a. `relevel()`
  b. `reorder()`
  c. `factor()`

```{r}

# relevel()

data$trial_type_relevel <- relevel(data$trial_type, "stop") 
xtabs(~ trial_type + trial_type_relevel, data)

# reorder()

data$trial_type_reorder <-  reorder(data$trial_type, data$perc_cor) # in this case, I'm using the default function "mean"                                                                          because there are the same number of observations. What                                                                       reorder() does, is it goes through all factors and                                                                           orders based on what you set the function to (i,e.,                                                                          mean, length, etc.)

xtabs(~ trial_type + trial_type_reorder, data)

# factor()

data$trial_type_factor <- factor(data$trial_type, levels = c("stop", "go")) # this is the most concrete way to set the order                                                                               of your factors. Be careful that you don't add                                                                               something that is not already there, or that                                                                                 you don't forget something that is present in                                                                                the dataset as this will lead to the generation                                                                               of NA's
xtabs(~ trial_type + trial_type_factor, data)

```

6. Missing values
  a. Do you have any missing values (NA) in your data?
  b. Are there any places where you *should* have missing values but they were read into R as some other value?
  c. If the answer to (b) is "yes", figure out how to read in your data in a way that correctly identifies the missing value "code"
  d. If you have any NAs in your data, describe why you think those values are missing. Does there appear to be any systematic relationship between missingness and other variables in your data?

```{r}
# a. I have no missing values (NA) in my data
# b. I shouldn't have missing values, because this data was cleaned in the process of converting it from Neuroexplorer to the CSV file
# c. N/A
# d. N/A

# summary(data) would be a good way to check for NA's
# If you want to be more specific, use is.na() for a specific column
# - data[is.na(data$trial_type), ]
```

