---
title: "Day 7 Homework"
output: html_document
---

Find three relationships in your data.  For each relationship, do the following:

1. Verbally articulate the relationship you want to examine with a plot.

      Comparison 1 - compare the distribution movement times by trial type
      Comparison 2 - difference in movement times by trial type
      Comparison 3 - difference in movement times by performance and trial type
      

2. Verbally identify what variables you want to map to each graphical dimension.

      Comparison 1 - density plot percent cor on x-axis; mt of y-axis
      Comparison 2 - boxplots showing 4 possible comparisons (x-axis trial types -whether correct or incorrect, y axis- mt)
      Comparison 3 - line graph (x-axis: trial type, y-axis: movement times split by performance)
      
      
3. Reshape your data as needed.

```{r}

###################
# Clear environment

rm(list = objects())

##############
# Load library

library(dplyr)
library(tidyverse)

##############
# Read in data

data <- read.csv("Brockett_HW_Dataset.csv", header = TRUE)
summary(data)
nrow(data)

mydata <- data

# Convert data into long format using gather

mydata.long <- gather(mydata, performance, movement_time, mt:er_mt)

# Create factors replacing mt and er_mt with correct and error

mydata.long$performance <- as.factor(ifelse(test = mydata.long$performance == "mt", yes = "correct", no = "error"))

# Subset data to test perc_cor by animal and generate new dataframe for analysis

perc.cor.by.animal <- group_by(mydata.long, trial_type, animal_id) %>% summarize(perc_cor = mean(perc_cor, na.rm = TRUE))
as.data.frame(perc.cor.by.animal)

# Subset data to test movement time by animal and generate new dataframe for analysis

mt.means.by.animal <- group_by(mydata.long, trial_type, performance, animal_id) %>% summarize(mt = mean(movement_time, na.rm = TRUE))
as.data.frame(mt.means.by.animal)

```

4. Use ggplot2 to create your graphs.

```{r}

# Comparison 1

ggplot(mydata.long, aes(x = movement_time)) + 
          geom_density(aes(fill = trial_type), alpha = .3) 



# Comparison 2

ggplot(data = mt.means.by.animal, aes(x = trial_type, y = mt, color = performance)) + 
          geom_boxplot() 

  

# Comparison 3

ggplot(data = mt.means.by.animal, aes(x = trial_type, y = mt, color = performance, group = performance)) + 
          stat_summary(fun.y = mean, geom = "point") +
          stat_summary(fun.y = mean, geom = "line") 
 


```

5. Fiddle with colors, axis labels, themes, etc. until the plot looks "publication ready" to you.  Try to change at least one thing per plot.

```{r}

# Comparison 1

comp1 <- ggplot(mydata.long, aes(x = movement_time)) + 
          geom_density(aes(fill = trial_type), alpha = .3) +
          xlab("Movement Time (s)") +
          ylab("Density") +
          scale_fill_brewer(palette = "Set1", name = "Trail Type") 
        

print(comp1)

# Comparison 2

comp2 <- ggplot(data = mt.means.by.animal, aes(x = trial_type, y = mt, color = performance)) + 
          geom_boxplot() +
          xlab("Trial Type") +
          ylab("Movement Time (s)") +
          scale_color_brewer(palette = "Set1", name = "Performance") 

print(comp2)   

# Comparison 3

library(Rmisc)

mt_descriptives <- summarySEwithin(mt.means.by.animal, measurevar = "mt", withinvars = c("trial_type", "performance"), idvar = "animal_id")
mt_descriptives


comp3 <- ggplot(data = mt_descriptives, aes(x = trial_type, y = mt, color = performance, group = performance)) + 
          stat_summary(fun.y = mean, geom = "point") +
          stat_summary(fun.y = mean, geom = "line") +
          geom_errorbar(width = .1, aes(ymin = mt - se, ymax = mt + se)) +
          xlab("Trial Type") +
          ylab("Movement Time") +
          scale_color_brewer(palette = "Set1", name = "Performance")
 
print(comp3)

```

6. Save all plots to a format that you could use in a paper.  HINT: PNG works well for pasting into Word documents.

```{r}

png()

comp1
comp2
comp3

dev.off()

```

